A Geometry for Network Visualization in \MakeLowercase{\texttt{ggplot2}}

### 2015-03-18 CC/writeup.Rnw
haven't pushed in a while

\maketitle
\begin{abstract}
Abstract will be here
\end{abstract}
<<chunk_setup, echo=FALSE>>=
opts_chunk$set(tidy = TRUE, echo=FALSE, message = FALSE, fig.height = 4, fig.width = 4, fig.align = 'center')
@
<<readingdata>>=
 library(knitr)
 library(ggplot2) # needs to be the version with geom_net! 
 theme_net <- theme(aspect.ratio = 1, line = element_blank(), panel.background = element_blank(), plot.background = element_blank(), axis.text=element_blank(),axis.title=element_blank())
 data(blood, football, theme_elements)
 email.net <- read.csv("~/Dropbox/ggplot2/email-data.csv") 
 email.names <- data.frame(name = as.factor(unique(c(as.character(email.net$From),as.character(email.net$to))))) 
@

@@

<<theme_ex>>=

@@

  \emph{Note: would be best with coloring vertices by conference} \citet{football}
% # <<football_ex>>=
% # ggplot(data = football$edges, aes(from_id = from, to_id = to)) + geom_net(vertices = football$vertices) + expand_limits(x = c(-2.5,2.5), y = c(-2.5,2.5)) + theme_net
% # @

@@

  \emph{Note: data set has edge weightings for number of co-occurences of characters. esize would be useful here!}
% <<lesmis_ex>>=
% ggplot(data = lesmis$edges, aes(from_id = from, to_id = to)) + geom_net(vertices = lesmis$vertices, aes(esize = value), layout = 'fruchtermanreingold') + expand_limits(x = c(-25,25), y = c(-25,25)) + theme_net
% @

>>>>

\maketitle
\begin{abstract}
Abstract will be here
\end{abstract}
<<chunk_setup, echo=FALSE>>=
opts_chunk$set(tidy = TRUE, echo=FALSE, eval = FALSE, message = FALSE, fig.height = 4, fig.width = 4, fig.align = 'center')
@
<<readingdata>>=
 library(knitr)
 library(ggplot2) # needs to be the version with geom_net! 
 theme_net <- theme(aspect.ratio = 1, line = element_blank(), panel.background = element_blank(), plot.background = element_blank(), axis.text=element_blank(),axis.title=element_blank())
 data(blood, football, theme_elements, lesmis)
 email.net <- read.csv("~/Desktop/NetworksResearch/ggnet/CC/data/email-data.csv") 
 email.names <- data.frame(name = as.factor(unique(c(as.character(email.net$From),as.character(email.net$to))))) 
@

@@

<<theme_ex, echo=TRUE, fig.cap= 'Inheritance structure for \\texttt{theme} elements in \\texttt{ggplot2}.'>>=

@@

  \emph{Note: would be best with coloring vertices by conference} 
  This next example comes from M.E.J. Newman's network data web page \citep{football}.  It is an undirected network consisting of all regular season college football games played between Division I schools in Fall of 2000.  There are 115 vertices and 613 edges: each vertex represents a school, and an edge represents a game played between two schools.}  
<<football_ex, echo=TRUE, fig.cap="All regular season Division I college football games in the Fall 2000 season.">>=
ggplot(data = football$edges, aes(from_id = from, to_id = to)) + geom_net(vertices = football$vertices, ealpha = 0.1) + expand_limits(x = c(-2.5,2.5), y = c(-2.5,2.5)) + theme_net
The network of football games is given in figure \ref{fig:football_ex}.

@@

  \emph{Note: data set has edge weightings for number of co-occurences of characters. esize would be useful here!}}
<<lesmis_ex, echo=TRUE, fig.cap="Coappearance network of characters in Victor Hugo's \\emph{Les Mis\\'{e}rables}">>=
ggplot(data = lesmis$edges, aes(from_id = from, to_id = to)) + geom_net(vertices = lesmis$vertices, aes(esize = value), layout = 'fruchtermanreingold') + expand_limits(x = c(-25,25), y = c(-25,25)) + theme_net
